---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(csatimer)

```

# csatimer

`csatimer` provides data on how much air time French politician receive in the media. 

The dataset contained in the package are also [available](https://github.com/benjaminguinaudeau/csatimer/tree/master/inst/csv) in the csv-format.

## Installation

``` r
# install.packages("devtools")
devtools::install_github("benjaminguinaudeau/csatimer")
```

## Data

*Last Update: January, 23 2022* 

Two types of datasets are provided: 
  
  * speaking time of politicians during routine period (no electoral campaigns)
  * speaking time of candidates during political campaigns
  
### Routine period (no electoral campaigns)

Every month, the [CSA](https://www.csa.fr/csapluralisme/tableau) collects how long each political personality speaks on each of the major radio and TV stations. 

This dataset can be accessed using `read_csa_routine` and is continuous between September 2017 and November 2021. 

```{r}
read_csa_routine() %>%
  dplyr::glimpse()
```


It contains the following columns: 
  
  * month <date> `"2017-01-01"`
  * station <chr> `"TF1", "France 2", "France Inter", ...`
  * prog_type <chr> `"JT", "MAG", "PROG"`
  * name <chr> `"Emmanuel Macron", "Marine Le Pen", "François Hollande", ...`
  * label <chr> `"Président", "Parti Socialiste", "Ministre", "Les Républicains", ...`
  * party <chr> `"Exécutif" , "Ps", "LR", ...`
  * time <dbl> 
  
Speaking times are measured in minutes. For instance, in September 2017, Emanuel Macron spoke 8.4 minutes on TF1.
  
`prog_type` refers to different types of TV/Radio shows: 

  * `JT`: newscast
  * `MAG`: political shows
  * `PROG`: non-political shows
  
### Electoral campaigns

During electoral campaigns - presidential, legislative and local - , the CSA publishes air time of campaigning candidates [data](https://www.csa.fr/Proteger/Garantie-des-droits-et-libertes/Proteger-le-pluralisme-politique/Pendant-une-election) *every two weeks*. 

For each candidate, three different measures are computed: 

  * `time_candidat`: speaking time of the candidate themselves
  * `time_support`: speaking time of personalities supporting the candidate
  * `time_mention`: speaking time of journalists mentioning the candidate

This dataset can be accessed using `read_csa_election("pres_2022")`. 

Following elections are available: 

  * Presidential elections 2022: `read_csa_election("pres_2022")`
  * Presidential elections 2017: `read_csa_election("pres_2017")`

```{r}
read_csa_election("pres_2022")  %>%
  dplyr::glimpse()
```

### Updating data

Data will be updated as the CSA publishes new routine and campaign data. 

To update the data local version, use `update_csatimer()`

```{r}
# Updating data
update_csatimer()
```

